Burst detection

Trying to make sense of the different methods posted in

github.com/ellesec/burstanalysis

This guy was trying to reproduce the thing and had a hard time too...

<https://github.com/StefanoBuccelli/burst_detection>

Of note, some of these functions are trying to use `fit.hsmm`, a function from a supposed `burstHSMM` package that cannot be found.

A "copy" of the package can be found in this link <http://www2.stat.duke.edu/~st118/Software/burstHSMM/>, which has only one function!

The function itself can be found in this link <http://www2.stat.duke.edu/~st118/Software/burstHSMM/R/burstHSMM.R>

I added it to the repo because it makes no sense to have it separate. It's on `HSMM_method.R`

```{r}
library(tidyverse, warn.conflicts = F)

# It's not clear what these files have...
# the "spikes" slot has values, what are they? ISIs ?
#spikes_filelist <- list.files(path = "../hiPSC_recordings",
#                              pattern = "h5", full.names = T)
#spike_list <- purrr::map(spikes_filelist, function(tt) rhdf5::h5read(tt, "spikes"))

# Go for the simulated data
load("../Simulation_results/sim_data.RData")
sim.data$reg.bursting[[1]] %>% str
```

```{r}
reg_bursts <- sim.data$reg.bursting
ggplot() +
  geom_point(aes(x=reg_bursts[[1]]$spks, y=1), pch="|", size=5)+
  geom_segment(aes(x=reg_bursts[[1]]$burst.beg, 
                   xend=reg_bursts[[1]]$burst.end,
                   y=1, yend=1),
               lwd=2,
               color="red")+
  xlim(c(0,20))


```

```{r}
qq <- logisi.pasq.method(sim.data$reg.bursting[[1]]$spks) %>%   as_tibble() %>% 
  mutate(beg_time = sim.data$reg.bursting[[1]]$spks[beg],
         end_time = sim.data$reg.bursting[[1]]$spks[end])
```

```{r}
foodwebr::foodweb(FUN="logisi_pasq_method")
```
